---
title: "Practical Machine Learning Course Project"
author: "jamesmcm"
date: "07/12/2014"
output: html_document
---

In this project we will use accelerometer data from http://groupware.les.inf.puc-rio.br/har and attempt to predict the manner in which they did the exercise.

```{r}
dftrain<-read.csv("./pml-training.csv")
dftest<-read.csv("./pml-testing.csv")

mycols <- NULL
for (i in 1:length(names(dftrain))){
if (class(dftrain[,names(dftrain)[i]])=="numeric" & any(is.na(dftrain[,names(dftrain)[i]]))==F ){
  mycols<-c(mycols,names(dftrain)[i])
}  
}
mycols<-c(mycols,"classe")
newdftrain<-dftrain[,mycols]
```
We use a random forest classifier on the numeric features without missing values, this results in 27 predictor variables, and the classe class variable:

`r mycols`


```{r eval=FALSE}
set.seed(101)

library(caret)

fit1 <- train(classe ~ ., data = newdftrain, method = "rf")
```
We obtain the following Random Forest model:

    Random Forest 

    19622 samples
       27 predictors
        5 classes: 'A', 'B', 'C', 'D', 'E' 

    No pre-processing
    Resampling: Bootstrapped (25 reps) 

    Type of random forest: classification
    Number of trees: 500
    No. of variables tried at each split: 2

    mtry  Accuracy   Kappa      Accuracy SD   Kappa SD    
    2    0.9932632  0.9914794  0.0008701709  0.001100304
   

    Confusion matrix:

         A    B    C    D    E  class.error
    A 5577    2    0    0    1 0.0005376344
    B   10 3778    9    0    0 0.0050039505
    C    0   10 3396   16    0 0.0075978960
    D    0    0   19 3194    3 0.0068407960
    E    0    0    1    6 3600 0.0019406709


The out of sample error can be approximated by the out of bag error, computed over the 25 resamples as cross-validation:

    OOB estimate of  error rate: 0.39%


The predictions for the test set were computed as follows:

```{r eval=FALSE}
answers<-NULL
for (i in 1:20){
answers<-c(answers,as.character(predict(fit1, dftest[i,])))
}

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(answers)
```

